\mbox{TRITON: Neural Neural Textures for Better Sim2Real}

### 2022-06-25 CORL/example.tex
Branchini\

\usepackage[preprint]{corl_2022} % Use this for the initial submission.
% \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{array, booktabs, ragged2e}
\usepackage{comment}

@@

% \title{TRITON: Globally Consistent Sim-to-Real Transfer
\title{Neural Neural Textures Make Sim2Real Consistent}
% \title{Neural Texture Fields from Unpaired Images for Better? Realistic? Sim2Real}
%``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
%via Neural Textures

\author{%
	Ryan Burgert \quad Jinghuan Shang \quad Xiang Li \quad Michael S. Ryoo\\
	Department of Computer Science\\
	Stony Brook University\\
	Stony Brook, NY 11794 \\
	\texttt{\{rburgert,jishang, xiangli8, mryoo\}@cs.stonybrook.edu} \\
	% \And
	% Michael Ryoo \\
	% Department of Computer Science\\
	% Stony Brook University\\
	% Stony Brook, NY 11794 \\
	% \texttt{mryoo@cs.stonybrook.edu} \\
	%\And
%	Emma Burgert \\
%	Ryan Burgert's Dog\\
}

@@

\vspace{-8pt}
\paragraph{Neural Textures}
\citet{deferred_neural_rendering} introduced the concept of neural textures and image translators in the context of a deferred rendering pipeline, used in other works such as \cite{surgical_video_translation} which is closely related to our project. 
\citet{surgical_video_translation} differs from TRITON in a few very important aspects though, the biggest being that it only synthesizes new camera views, where the only difference between each scene is the placement of the camera. In contrast, our algorithm takes in scenes where several objects are placed in different places or deformed, so that one static  global 3d model of the environment is not sufficient to accomplish our tasks. In addition, TRITON uses a new type of neural texture called a ``neural neural texture'', which is represented continuously using a fourier feature network, as described in \citet{fourier_feature_networks}.

@@

% %===============================================================================
\vspace{-8pt}
\section{Method} \label{sec:method}
	\begin{figure}[thbp]
	    \vspace{-15pt}
		\begin{center}
			% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
			% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
			\includegraphics[width=0.9\textwidth]{../images/main_diagram_beautiful.pdf}
		\end{center}
		\vspace{-10pt}
		\caption{
			% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
			% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
			% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
			% $N$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
			%
			%JUNE 12:
			%Don't say 4 main components; say 2 components and 2 losses
			%TODO: Try to use right-angled arrows
			%TODO: Use tau as a function
			%Copy paste the figure multiple times, deleting things
			%Mention "Neural Neural Texture": Its a function mapping UV to RGB
			%Formulation doesnt mentino texture; just uvl inputs and final outputs
			%Always use function notation tauuv instead of just tau (in figure as well) 
			%The arrow should be running through tau. It's not a variable its a function...
			%Rename 'B' to "N" for batch size
			%Figure 8: Align consistent with inconsistent and use all 5 green ones
			%
			This figure is an overview TRITON.
			Inputs are on the left, and outputs are on the right.
			The dashed arrows indicate losses.
			Although $\pi\toN$ and $\ph\toN$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
			% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
			% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
			% TODO: Use variables instead of 3,4
			% TODO: Make the text larger and easier to read
			% TODO: Simplify the diagram?
		}
		\label{fig:main_diagram}
	\end{figure}
		In this section, we describe how TRITON works to translate images from domain A (simulation) to domain B (photos) while maintaining surface consistency. 
		TRITON introduces a learneable neural neural texture with two novel surface consistency losses to an existing image translator. In the end, TRITON is able to effectively generate photorealistic images.
		%JUNE 12:
		%TODO: MIgrate all four of these teasers into their respective subsections to save space.
\vspace{-3pt}
	\subsection{Neural Neural Texture Projection}
	\label{sec:neural_tex}
	\vspace{-3pt}
		\begin{figure}[t]
		    \vspace{-5pt}
			\begin{center}
				\includegraphics[width=0.8\textwidth]{../images/learnable_textures.pdf}
			\end{center}
			\vspace{-3pt}
			\caption{
				This figure details how our neural neural textures are calculated in Figure~\ref{fig:main_diagram}. They are fully differentiable, and represented continuously along the texture's u and v axes using Fourier feature networks.
			}
			\vspace{-3pt}
			% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
			% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
			% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
			\label{fig:learnable_textures}
		\end{figure}

@@

		% For our purposes, MS-SSIM is a metric that measures the similarity of two BCHW tensors on a scale from 0 to 1.
		% Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - \text{msssim}(x,y)$. 
		We define an image similarity loss $\similar$ between two images $x,y$ that returns a score between -1 and 1, where 0 means perfect similarity:
		\begin{equation}
			\similar(x,y) = L_2(x,y)-\msssim(x,y) 
		\end{equation}
		This function combines mean pixel-wise $L_2$ distance (used in MUNIT) with multi-scale structural image similarity $\msssim$, introduced in \citep{msssim}. Note that this loss can also be applied to the latent representations obtained by $E_A$ and $E_B$, because like images those tensors are also three dimensional.

@@

	%===============================================================================
\vspace{-8pt}
\section{Experiments}\label{sec:results}
\vspace{-3pt}
\subsection{Datasets}
\label{sec:datasetsresults}
\vspace{-2pt}
%Here we detail the datasets used in our experiments.
% We constructed multiple datasets for our experiments.
We constructed two datasets AlphabetCube-3 and RobotPose-xArm to benchmark different image translators in many perspectives.
In our setting, each dataset is composed of two sets of unpaired images: UVL scenes from a simulator and real photographs.
Note that the images in all datasets are unpaired and UVL scenes only rely on rough 3d models of the objects in the scene without need of precisely aligning objects in the simulator to the real world.
% . They are all unpaired, and have RGB values ranging from 0 to 1.
We use AlphabetCube-3 for image translation quality evaluation, and RobotPose-xArm for sim2real policy learning evaluation.

@@

%\subsection{Qualitative Evaluation Results}
%We show qualitative evaluation results ....[TODO]
\begin{figure}[th]
	\begin{center}
		\includegraphics[width=.9\textwidth]{../images/frame_inconsistency_diagram.png}
	\end{center}
	\vspace{-7pt}
	% Each outline color corresponds to the same cube.
	% The same cubes are marked with the same colored outlines across all photos.
	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
	\caption{
	    Comparison of image translation methods.
	    The first column is the UVL map as the input.
	    The other columns are results using different image translation methods.
		Each row of images shows a different random placement of objects in the scene.
		TRITON consistently outputs high quality results over different object arrangements. 
		``TRITON Texture-Only'' stands for TRITON without two surface consistency losses $\lUC$ and $\lTR$.
		% Each column of images is a different image translation algorithm.
		% The same cube is marked with the same color outline across all photos.
		% TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
		% Meanwhile, CycleGAN for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
		% Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
		% CUT and CycleGAN are not consistent, while TRITON is.
		% TODO: Update the images in this to have the latest training iteration...
		}
		\vspace{-15pt}
		\label{fig:frame_inconsistency_diagram}
	\end{figure}

@@

% TODO: Explain what sync and unsync mean, retrieve the results for CycleGAN and CUT
\vspace{-5pt}
\subsection{Sim2real Transfer for Robot Learning}
\begin{figure}[thbp]
    \centering
    \vspace{-10pt}
    \includegraphics[width=.8\textwidth]{../images/sim2real_framework.pdf}
    \vspace{-10pt}
    \caption{Sim2real framework of using TRITON. We evaluate in two settings: Seen and Unseen. In Unseen, we use a new camera viewpoint to train and evaluate the policy. This new viewpoint is not used for training TRITON. }
    \vspace{-5pt}
    \label{fig:sim2realframework}
\end{figure}
In this section we demonstrate how TRITON improves sim2real transfer for robot policy learning. To this end, we first train TRITON on a dataset consist of unpaired UVL scenes from a robot simulator (Gazebo) and photos from the real robot. Once TRITON is trained, we learn the robot policy while only utilizing the simulator. The input of the policy is the fake photo $\ph$ translated from the simulated UVL scene using TRITON's translator $T_{A\to B}$. Finally, the trained policy is directly evaluated on the real robot, taking real photos $p$ as input.

@@

\textbf{Task} We use a robot pose imitation task for our experiments. Given the input of a photo of real robot pose, the policy outputs robot controls to replicate that target pose. We measure the angular error between the replicated and target poses as our evaluation metric:$\sqrt{\sum_{j} (\hat{a}_j - a_j)^2}$,
where $\hat{a}_j$ and $a_j$ are replicated and target joint angles respectively, and $j$ is the joint index. We use an xArm robot which has seven joints. We also attached patterns and tapes on the robot to make its texture more challenging to model.

@@

\begin{figure}[tbhp]
    \centering
    \vspace{-3pt}
    \includegraphics[width=\textwidth]{../images/sim2real_res.pdf}
    \vspace{-5pt}
    \caption{Evaluation results of sim2real robot learning. We compare TRITON against two baselines and one TRITON variant w/o $\psi, \ell_{UC}, \ell_{TR}$ across 3 different input image resolutions. TRITON outperforms CycleGAN~\cite{cyclegan} and CUT~\cite{cut} consistently across (a) all resolutions and (b) unseen viewpoints. Results in (a) are from Seen setting only. Results in (b) are from 336x336 resolution. }
    \label{fig:sim2real}
    \vspace{-3pt}
\end{figure}

@@

\acknowledgments{We thank Srijan Das and Kanchana Ranasinghe for valuable discussions. This work was supported by the National Science Foundation (IIS-2104404 and CNS-2104416).}
%===============================================================================

@@

% \clearpage
% The acknowledgments are automatically included only in the final and preprint versions of the paper.

@@

% \clearpage

\input{appendix.tex}

\begin{comment}
\clearpage

\section*{Appendix} 
\label{sec:appendix}

@@

		TRITON is very robust to geometric imperfections. However, sometimes it takes this a bit too far - it can over-fit textures onto the wrong objects and still maintain consistency.
		In one example, it manages to map an apple texture onto a cube.

		To help TRITON correctly match textures to objects, we introduce a small amount of supervision by adding a color loss. I'm going to stop writing this because I don't know if I even want to keep this in the paper...you can achieve the same result by running the algorithm multiple times, and so its not strictly necessary.

@@

>>>>

\usepackage{corl_2022} % Use this for the initial submission.
% \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{array, booktabs, ragged2e}
\usepackage{comment}

@@

% \title{TRITON: Globally Consistent Sim-to-Real Transfer
\title{\mbox{TRITON: Neural Neural Textures for Better Sim2Real}
%``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
%via Neural Textures
}

\author{%
	Ryan Burgert \\
	Department of Computer Science\\
	Stony Brook University\\
	Stony Brook, NY 11794 \\
	\texttt{rburgert@cs.stonybrook.edu} \\
	% \And
	% Michael Ryoo \\
	% Department of Computer Science\\
	% Stony Brook University\\
	% Stony Brook, NY 11794 \\
	% \texttt{mryoo@cs.stonybrook.edu} \\
	\And
	Emma Burgert \\
	Ryan Burgert's Dog\\
}

@@

\vspace{-8pt}
\paragraph{Neural Textures}
\citet{deferred_neural_rendering} introduced the concept of neural textures and image translators in the context of a deferred rendering pipeline, used in other works such as \cite{surgical_video_translation} which is closely related to our project. 
\citet{surgical_video_translation} differs from TRITON in a few very important aspects though, the biggest being that it only synthesizes new camera views, where the only difference between each scene is the placement of the camera. In contrast, our algorithm takes in scenes where several objects are placed in different places or deformed, so that one static  global 3d model of the environment is not sufficient to accomplish our tasks. In addition, TRITON uses a new type of neural texture called a ``neural neural texture'', which is represented continuously using a fourier feature network, as described in \citep{fourier_feature_networks}.

@@

% %===============================================================================
\vspace{-8pt}
\section{Method} \label{sec:method}
	\begin{figure}[thbp]
	    \vspace{-15pt}
		\begin{center}
			% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
			% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
			\includegraphics[width=0.9\textwidth]{../images/main_diagram_beautiful.pdf}
		\end{center}
		\vspace{-10pt}
		\caption{
			% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
			% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
			% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
			% $N$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
			%
			%JUNE 12:
			%Don't say 4 main components; say 2 components and 2 losses
			%TODO: Try to use right-angled arrows
			%TODO: Use tau as a function
			%Copy paste the figure multiple times, deleting things
			%Mention "Neural Neural Texture": Its a function mapping UV to RGB
			%Formulation doesnt mentino texture; just uvl inputs and final outputs
			%Always use function notation tauuv instead of just tau (in figure as well) 
			%The arrow should be running through tau. It's not a variable its a function...
			%Rename 'B' to "N" for batch size
			%Figure 8: Align consistent with inconsistent and use all 5 green ones
			%
			This figure is an overview TRITON.
			Inputs are on the left, and outputs are on the right.
			The dashed arrows indicate losses.
			Although $\pi\toN$ and $\ph\toN$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
			% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
			% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
			% TODO: Use variables instead of 3,4
			% TODO: Make the text larger and easier to read
			% TODO: Simplify the diagram?
		}
		\label{fig:main_diagram}
	\end{figure}
		In this section, we describe how TRITON works to translate images from domain A (simulation) to domain B (photos) while maintaining surface consistency. 
		TRITON introduces a learneable neural neural texture with two novel surface consistency losses to an existing image translator. In the end, TRITON is able to effectively generate photorealistic images.
		%JUNE 12:
		%TODO: MIgrate all four of these teasers into their respective subsections to save space.
\vspace{-3pt}
	\subsection{Neural Neural Texture Projection}
	\vspace{-3pt}
		\begin{figure}[thbp]
		    \vspace{-5pt}
			\begin{center}
				\includegraphics[width=0.6\textwidth]{../images/learnable_textures.pdf}
			\end{center}
			\vspace{-3pt}
			\caption{
				This figure details how our neural neural textures are calculated in Figure~\ref{fig:main_diagram}. They are fully differentiable, and represented continuously along the texture's u and v axes using Fourier feature networks.
			}
			\vspace{-10pt}
			% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
			% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
			% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
			\label{fig:learnable_textures}
		\end{figure}

@@

		% For our purposes, MS-SSIM is a metric that measures the similarity of two BCHW tensors on a scale from 0 to 1.
		% Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - \text{msssim}(x,y)$. 
		We define an image similarity loss $\similar$ between two images $x,y$ that returns a score between 0 and 1, where 0 means perfect similarity:
		\begin{equation}
			\similar(x,y) = L_2(x,y)-\msssim(x,y) 
		\end{equation}
		This function combines mean pixel-wise $L_2$ distance (used in MUNIT) with multi-scale structural image similarity $\msssim$, introduced in \citep{msssim}. Note that this loss can also be applied to the latent representations obtained by $E_A$ and $E_B$, because like images those tensors are also three dimensional.

@@

	%===============================================================================
\vspace{-8pt}
\section{Experiments}\label{sec:results}
\vspace{-3pt}
\subsection{Datasets}
\vspace{-2pt}
%Here we detail the datasets used in our experiments.
% We constructed multiple datasets for our experiments.
We constructed two datasets AlphabetCube-3 and RobotPose-xArm to benchmark different image translators in many perspectives.
In our setting, each dataset is composed of two sets of unpaired images: UVL scenes from a simulator and real photographs.
Note that the images in all datasets are unpaired and UVL scenes only rely on rough 3d models of the objects in the scene without need of precisely aligning objects in the simulator to the real world.
% . They are all unpaired, and have RGB values ranging from 0 to 1.
We use AlphabetCube-3 for image translation quality evaluation, and RobotPose-xArm for sim2real policy learning evaluation.

@@

%\subsection{Qualitative Evaluation Results}
%We show qualitative evaluation results ....[TODO]
\begin{figure}[th]
	\begin{center}
		\includegraphics[width=.9\textwidth]{../images/frame_inconsistency.pdf}
	\end{center}
	\vspace{-7pt}
	% Each outline color corresponds to the same cube.
	% The same cubes are marked with the same colored outlines across all photos.
	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
	\caption{
	    Comparison of image translation methods.
	    The first column is the UVL map as the input.
	    The other columns are results using different image translation methods.
		Each row of images shows a different random placement of objects in the scene.
		TRITON consistently outputs high quality results over different object arrangements. 
		``TRITON texture only'' stands for TRITON without two surface consistency losses $\lUC$ and $\lTR$.
		% Each column of images is a different image translation algorithm.
		% The same cube is marked with the same color outline across all photos.
		% TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
		% Meanwhile, CycleGAN for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
		% Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
		% CUT and CycleGAN are not consistent, while TRITON is.
		% TODO: Update the images in this to have the latest training iteration...
		}
		\vspace{-15pt}
		\label{fig:frame_inconsistency_diagram}
	\end{figure}

@@

% TODO: Explain what sync and unsync mean, retrieve the results for CycleGAN and CUT
\vspace{-5pt}
\subsection{Sim2real Transfer for Robot Learning}
\begin{figure}[thbp]
    \centering
    \vspace{-10pt}
    \includegraphics[width=.8\textwidth]{images/sim2real_framework.pdf}
    \vspace{-10pt}
    \caption{Sim2real framework of using TRITON. We evaluate in two settings: Seen and Unseen. In Unseen, we use a new camera viewpoint to train and evaluate the policy. This new viewpoint is not used for training TRITON. }
    \vspace{-5pt}
    \label{fig:sim2realframework}
\end{figure}
In this section we demonstrate how TRITON improves sim2real transfer for robot policy learning. To this end, we first train TRITON on a dataset consist of unpaired UVL scenes from a robot simulator (Gazebo) and photos from the real robot. Once TRITON is trained, we learn the robot policy while only utilizing the simulator. The input of the policy is the fake photo $\ph$ translated from the simulated UVL scene using TRITON's translator $T_{A\to B}$. Finally, the trained policy is directly evaluated on the real robot, taking real photos $p$ as input.

@@

\textbf{Task} We use a robot pose imitation task for our experiments. Given the input of a photo of real robot pose, the policy outputs robot controls to replicate that target pose. We measure the angular error between the replicated and target poses as our evaluation metric:$\sqrt{\sum_{j} (\hat{a}_j - a_j)^2}$,
where $\hat{a}_j$ and $a_j$ are replicated and target joint angles respectively, and $j$ is the joint index. We use an xArm robot which has 7 joints. We also attached patterns and tapes on the robot to make its texture more challenging to model.

@@

\begin{figure}[tbhp]
    \centering
    \vspace{-3pt}
    \includegraphics[width=.95\textwidth]{images/sim2real_res.pdf}
    \vspace{-5pt}
    \caption{Evaluation results of sim2real robot learning. We compare TRITON against two baselines and one TRITON variant w/o $\ell_{UC}$ across 3 different input image resolutions. TRITON outperforms CycleGAN~\cite{cyclegan} and CUT~\cite{cut} consistently across (a) all resolutions and (b) unseen viewpoints. Results in (a) are from Seen setting only. Results in (b) are from 336x336 resolution. }
    \label{fig:sim2real}
    \vspace{-3pt}
\end{figure}

@@

@@

\clearpage
% The acknowledgments are automatically included only in the final and preprint versions of the paper.
\acknowledgments{}

@@

\begin{comment}

\clearpage

\section{Appendix} 
\label{sec:appendix}

@@

		TRITON is very robust to geomtric imperfections. However, sometimes it takes this a bit too far - it can overfit textures onto the wrong objects and still maintain consistency.
		In one example, it manages to map an apple texture onto a cube.

		To help TRITON correctly match textures to objects, we introduce a small amount of supervision by adding a color loss. I'm going to stop writing this because I don't know if I even want to keep this in the paper...you can achieve the same result by running the algorithm multiple times, and so its not strictly nessecary.

@@

\appendix

\section{Appendix}

\subsection{Neural Neural Textures: More Details}

	In Section \ref{sec:neural_tex}, we mentioned that neural neural textures learn better than raster neural textures. 
	TRITON can be ablated to use raster textures. Let's call this version ``Raster TRITON''. 
	Raster TRITON is extremely sensitive to the resolution of its neural texture, and can be numerically unstable if that resolution is too high.
	In comparison, regular TRITON's neural neural textures do not have a specific resolution: they are continuously defined over the UV domain using Fourier feature networks.

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=400pt]{../images/raster_texture_resolution_comparisons.pdf}
		\end{center}
		\caption{
			The resolution of the raster neural texture seriously impacts performance in ``Raster TRITON''. Each column has a different neural texture resolution.
			The neural texture only looks like the translation when the resolution is low.
		}
		\label{fig:raster_texture_resolution_comparisons}
	\end{figure}

	In this paragraph we offer possible explanations for these observations.
	With raster-based textures, only the side of an object that currently is seen in a view is allowed to change during each update, because the gradient can not be propagated into pixels which are not seen.
	If this means changing overall brightness of an object for example, the brightness of that object can not be changed over the entire object until every side has been seen - which will not happen in a single iteration, since the batch size is limited.

	In addition to not propagating the gradient to unseen sides of objects, it also can not propagate to texels in-between the UVL values seen in a scene image.
	When the raster neural texture is too large, aliasing effects occur: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.
	In practice, this makes large raster neural textures unstable and limits us to using small amounts of detail.
	With neural neural textures, this aliasing problem is mostly mitigated, because when a certain texture receives a gradient at particular UV coordinates, the areas of the texture between those coordinates are also changed.

\subsection{Unprojection Consistency Loss: More Details}

	Here, we give more details about unprojection consistency loss $\lUC$.

	The exact equation for $\lUC$ is as follows:
	to formally define $\lUC$ we define unprojections $\unprojection^{1...N,1...L}$ and mean unprojections (aka recovered textures) $\bar{\unprojection}^{1...L}$ 
	with each $\unprojection^{n,i}\in\real^{3\times128\times128}$:
	%Jinghyan's Version (uses expectation)
	% \begin{equation}
	% 	\unprojection_{U,V}^{n,i}=\expectation\ph_{x,y}^n 
	% 	\eqand \bar{\unprojection}^i_{u,v}   =   
	% 		\frac{1}{N} \lsum_n\unprojection^{n,i}_{u,v} 
	% 	\eqand 
	% 	%\lUC=\frac{\lsum_{i,U,V}
	% 	%\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2}}
	% 	%{128\cdot128\cdot L}
	% 	\lUC=\mathbb{E}\left[
	% 	\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2} \right]
	% \end{equation}
	%
	%
	%Unabbreviated: Not Jinguan's version; 
	\begin{multline}
		\unprojection_{c,U,V}^{n,i}=\expectation\ph_{c,x,y}^n 
		\eqand \bar{\unprojection}^i_{c,u,v}   =   
			\frac{1}{N} \lsum_{n=1}^N\unprojection^{n,i}_{c,u,v} 
		\eqand \\
		\lUC=\frac{\lsum_{i=1}^L\lsum_{c=1}^3\lsum_{U=1}^{128}\lsum_{V=1}^{128}
		\sqrt[]{\frac{1}{N}\lsum_{n=1}^N\left(\bar{\unprojection}^i_{c,u,v}-\unprojection^{i,n}_{c,U,V}\right)^2}}
		{3\cdot128\cdot128\cdot L}
	\end{multline}
	where $U=\lfloor128u\rfloor$ and $V=\lfloor128v\rfloor$ and $i=I(l)$ with
	%  $(u,v,l)=s^n_{1...3,x,y}$
	$u=s^n_{1,x,y}$, $v=s^n_{2,x,y}$, $l=s^n_{3,x,y}$
	for all 
	$n \in \{1...N\}$ , 
	$i \in \{1...L\}$ , 
	$x \in \{1...W\}$ , 
	$y \in \{1...H\}$ , 
	$U \in \{1...128\}$ , 
	$V \in \{1...128\}$.

	\bigskip

	The hyperparameter 128 we described in Section \ref{sec:unprojection_consistency_loss} refers to the resolution of the unprojections used to calculate $\lUC$.
	In Figure \ref{fig:unprojection_resolution_comparison} we see that if we were to set it higher, the gradient wouldn't affect the neural texture as densely.

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=400pt]{../images/unprojection_resolution_comparison.pdf}
		\end{center}
		\caption{
			Here, we unproject a single fake photo $\ph^i$. The resolution of the unprojection matters for unprojection consistency loss. The larger it is, the more precise the alignment will be but the less likely a given UV value is to be assigned a loss greater than 0, creating numerical instability and slowing down learning. 
			When the unprojection resolution is too high, only a few areas of the neural texture will receive a gradient during backpropogation. In practice we use the resolution $128\times128$.
		}
		\label{fig:unprojection_resolution_comparison}
	\end{figure}

\subsection{Training Procedures}

	In this section we detail the training procedures used to create results in Section \ref{sec:results} from Triton, CycleGAN, CUT,
		TRITON w/o $\lUC,\lTR$ (aka TRITON with neither unprojection consistency loss nor texture reality loss), and
		TRITON w/o $\psi, \lUC,\lTR$ (aka TRITON without textures, and therefore also without unprojection consistency loss or texture reality loss).

	\subsubsection{TRITON}
	\label{par:triton}
	We train TRITON for 200,000 iterations on all datasets. This takes about 36-48 hours on an NVIDIA RTX A5000. 
	The dimension of each input scene is defined by hyperparameter height $H$; the width is scaled to match the aspect ratio of the original input.
	To avoid running out of video memory, we randomly crop each input to a $256\times256$ subset and run TRITON on that cropped input.
	We use batch size 5 during training.

	We found that the best way to train TRITON is to start with smaller $H$ values and progressively increase that value during training.
	For the first 50,000 iterations we use $H=320$, then for the next 50,000 iterations $H=420$, then for the last 100,000 iterations $H=\text{(the height of the original input scene)}$.

	Like in \cite{surgical_video_translation}, we use three Adam optimizers: two for the translation module's encoders and decoders, and another for the neural texture.
	For the translation module's optimizers, we use learning rate $\num{1e-4}$, and for the neural neural texture we use learning rate $\num{1e-3}$. 
	Every 100,000 iterations all learning rates are halved.

	During evaluation, we render the neural neural texture onto a raster grid of pixels. Because the neural neural texture has a 2d manifold, it can be closely approximated by an RGB image. Using this method lets us avoid evlauating $\psi$'s fourier feature network on every frame by using a raster image as a lookup table. This decreases video memory usage and speeds up calulations during inference.

	\subsubsection{TRITON w/o $\lUC,\lTR$}
	\label{par:triton_without_luc}
	This ablation is also known as ``Texture-Only'' TRITON, because it has a learnable texture $\psi$ but no consistency losses.
	Its trained the same way that we train TRITON normally as discussed above in \ref{par:triton}, except the surface consistency losses $\lUC$ and $\lTR$ are omitted.
	Effectively, it performs better than MUNIT-like TRITON (aka TRITON w/o $\psi, \lUC,\lTR$, discussed in \ref{par:munit_triton})
	% It still has a learnable texture $\psi$ though, which is allowed to change however it likes.

	\subsubsection{TRITON w/o $\psi, \lUC,\lTR$}
	\label{par:munit_triton}
	This ablation is very similar to MUNIT, as TRITON is based on MUNIT and this ablation has neither learnable texture nor consistency losses.
	Like in subsection \ref{par:triton_without_luc}, this ablation shares the same training procedures as TRITON.

	\subsubsection{CycleGAN}
	\label{par:cyclegan}
	We use the original implementation of CycleGAN, and stick to the reccomended 200 epochs, as it tends to overfit if you go further. 
	For our tests, we run CycleGAN on multiple different scales of the input scenes, with input sizes $286\times286$ (CycleGAN's default), $320\times320$, $420\times420$ and $512\times512$. 
	After translation, we stretch the image into the input's aspect ratio.
	We also set $\lambda_{identity}=0$, meaning we disable the identity loss.
	The reported results are the calculated using the best results among these resolutions.
	This dramatically improves CycleGAN's performance when translating UVL scenes to photographs, as this loss was built with the assumption that some parts of the input should not be changed during translation (which is not true in our case).

	\subsubsection{CUT}
	\label{par:cut}
	We use the original implementation of CUT, and stick to the recommended 400 epochs, as it tends to overfit if you go further. 
	Like with CycleGAN in \ref{par:cyclegan}, we run CUT on multiple different resolutions of the input scenes, with input sizes $286\times286$ (CUT's default), $320\times320$, $420\times420$ and $512\times512$. 
	After translation, we stretch the image into the input's aspect ratio.
	The reported results are the calculated using the best results among these resolutions.

\subsection{More Results}

	\subsubsection{Unprojection Comparisons}

		In this section we expand on the results in Subsection \ref{sec:datasetsresults} by showing the mean unprojection (aka recovered texture) for different image translation algorithms. With the 14 UVL images and corresponding fake photos (or photos) as calculated in \ref{sec:datasetsresults}, we average their unprojections.
		If a translation algorithm is consistent, these unprojections should align well and the average $bar{\omega}$ should not be blurry.

		\begin{figure}[H]
			\begin{center}
				\includegraphics[width=400pt]{../images/unprojection_comparisons.pdf}
			\end{center}
			\caption{
				In this figure, we compare the recovered textures $\bar{\omega}$ (aka mean unprojections) of the 14 labeled images between different algorithms, and compare it to a ground truth. In this diagram, we align all the unprojections to make them easier to compare. Note how TRITON is more crisp and matches the unprojected photographs better than the other algorithms, which are blurrier and have the wrong colors and letters on each side of the alphabet blocks. CycleGAN and CUT for example incorrectly duplicate letters between alphabet blocks.
			}
			\label{fig:unprojection_resolution_comparison}
		\end{figure}

\pagebreak
	\subsubsection{Videos}

		In this section we have links to animations that help demonstrate various aspects of TRITON.
		If you are viewing this document on a computer, click a thumbnail to view the video.

		% https://youtu.be/fuTSta_M6NQ

		\begin{figure}[H]
			\begin{center}
			\href{https://youtu.be/kecK_cJgLT8}{
					\includegraphics[width=300pt]{../images/robot_arm_animation_thumbnail.png}
					}
				\end{center}
			\caption{
				This animation shows a side-by-side comparison of different camera viewpoints of the results discussed in Section \ref{sec:robotarm_results}, as well as the inputs, ground truth video, TRITON and TRITON ablation videos.
				Url: \href{https://youtu.be/kecK_cJgLT8}{youtu.be/kecK\_cJgLT8}
			}
			\label{fig:robotarm_anim}
		\end{figure}

		\begin{figure}[H]
			\begin{center}
			\href{https://youtu.be/0t0xiVS_8D0}{
					\includegraphics[width=300pt]{../images/algo_comparison_thumbnail.pdf}
					}
				\end{center}
			\caption{
				This animation shows an animation of various algorithms on a dataset with 5 alphabet blocks moving around. 
				When watching, note how the numbers on the top of the cubes in both CycleGAN and CUT change over time, while with TRITON they stay the same.
				Url: \href{https://youtu.be/0t0xiVS_8D0}{youtu.be/0t0xiVS\_8D0}
			}
			\label{fig:algocomparisonvideo}
		\end{figure}

		\begin{figure}[H]
			\begin{center}
			\href{https://youtu.be/0t0xiVS_8D0}{
					\includegraphics[width=300pt]{../images/ThreeDatasets.png}
					}
				\end{center}
			\caption{
				This video shows the results of TRITON applied on three of the datasets shown in Figure \ref{fig:first_diagram}.
				The top row shows the input scenes $s$, and the bottom row shows the fake photographs $\ph$.
				Url: \href{https://youtu.be/0t0xiVS_8D0}{youtu.be/0t0xiVS\_8D0}
			}
			\label{fig:algocomparisonvideo}
		\end{figure}
